\documentclass[12pt]{article}

\usepackage[paperwidth=8.5in,paperheight=11in,top=.75in,left=.75in,right=.75in,bottom=.75in]{geometry} 

\usepackage{benj,abbrevs}

\usepackage{txfonts}

\begin{document}

\subsection*{Budget justification}

\subsubsection*{Personnel costs}

I have requested the standard departmental rate, \$17,500 per year, to hire a University of Toronto doctoral student as a research assistant over the full term of the project. There are a number of doctoral students in my department that have research interests suitably related to the themes of my project. 

The central duty of the research assistant will be to help me research literature that is relevant to the project. As the relevant literature spans various subfields of philosophy over much of the last half century, the assistance of the research assistant will be critical. They will track down references and write detailed reviews of the most important papers that they identify. They will also compile a master bibliographic file for all of the sources relevant to the project, including many papers I have already identified. This assistance will significantly increase the rate at which my project proceeds.

Our regular discussion of the literature will also very likely lead to opportunities for collaborative work between myself and the research assistant. There are many topics closely related to this research project that I will encourage my research assistant to explore, and which have the potential to lead to several co-authored papers.

I will also rely on the research assistant for editorial assistance. They will be responsible for manuscript preparation and proofreading of articles when they are prepared for submission to journals, and when the final proofs get returned for checking. This will also help the research assistant learn about the publication process, and will help them prepare for publishing their own work.


\subsubsection*{Travel and subsistence costs}

I have budgeted \$1,000 per year for my own travel within Canada to present results from the project, primarily at meetings of the Canadian Philosophical Association (an average of \$500 airfare and ground transportation, \$400 for 3 days in a hotel, and \$100 for three days of meals). Any left over funds from this category will be used for minor research related travel costs. In particular they will be used for short trips to meet with scholars working on related issues at other Canadian universities. For the third year of the project I have budgeted \$4,500 to cover travel to three major professional conferences and workshops in the US and Europe to present the results from the project. For the first, second, and fourth year, I have budgeted \$3,000 for two such trips. The additional trip in the third year reflects the triennial clock of the World Congress and School on Universal Logic (UNILOG): UNILOG is an ideal venue to present some of the results of this research.
 
I have estimated the average \$1,500 cost of trip as follows. Assuming an average trip length of three days, I expect average airfare and ground transport costs to be \$800, and I have additionally budgeted \$200 for meals and \$500 for a hotel over the three days. There are many different conferences where I expect to send my research to be considered for presentation. In addition to UNILOG, they include the Inland Northwest Philosophy Conference, the Society for Exact Philosophy, and the annual meetings of the American Philosophical Association and the Aristotelian Society--Mind Society Joint Session.

The budget also includes funds for the research assistant to join me on some of these trips. I have allotted \$1,500 for them to travel to at least two conferences outside of Canada that will be held during the term of the project. In addition I have also allotted \$1,000 for them to attend Canadian conferences in each of the years during the term of the project. These conferences will present critical networking opportunities for the student. I expect that by the final two years they will be presenting work of their own related to the research project.

 
% I have also budgeted an additional \$1000 for travel to meet with my collaborator Adam Russell Murray, at the University of Manitoba, in the second and fourth years (the cost breakdown is as for CPA travel), to engage in close, sustained discussion of the project (Murray may use his own funds to travel to meet me in the alternating years).


\subsubsection*{Other expenses}



I have a well-functioning laptop currently that is absolutely essential to my work. I anticipate that a few years into the project I will be in need of a replacement laptop. I have therefore budgeted \$2,500 in the third year of the project for the purchase of a new laptop and perhaps other related items.

I have also allocated \$250 per year to cover the purchase of books and monographs that I will need to use with regular frequency. While many texts can be obtained through the library, there are those that I will need throughout the project and so will need to purchase.


\end{document}

